---
title: "配对交易研究"
output: html_notebook
---

初始化数据和变量
```{r}
source(file.path(substr(getwd(),1,22),"header.R"))
symA="600519.SH"
symB="000016.SH"

```


## 基本思路
1. 分析好的曲线和不好的曲线的区别
回撤的时候主要都是假突破，曲线在一个区间内震荡时间太久
计算过去6个月，在某个区间段的时间长度，以此作为是否会震荡很久的指标。将数据分成等区间的，然后求标准差，标准差越大则越分散，越不太可能在一个区间震荡。这个指标目标看是基本有效的。

```{r}
load(paste0(mypath.data,"sym50中性策略回测结果.RData"))


symA="601818.SH"
x<-get(symA)
idx.excess <- grep(paste0("excess", return.nDay, "D"), names(x))
excessPlot(symA,symB,60)
chart.CumReturns(get(paste0("R",symA)))

fsd<-function(sym){
  x<-get(sym)
idx.excess <- grep(paste0("excess", return.nDay, "D"), names(x))

  ss<-x[,idx.excess]
  ss<-as.numeric(unlist(x["2015/"]))
  qs<-quantile(ss,c(0.10,0.90),na.rm=T)
  ss<-ss[!is.na(ss)]
ee<-sd(unlist(table(cut(ss[ss>qs[1]&ss<qs[2]],100))))
ee
  
}

myfsd<-sapply(sym50,fsd)

sort(myfsd,decreasing = T)

```

2. 优化曲线的进场和离场时点
将SMA换成VMMA，VMMA还没有思路做，用EMA代替
EMA有时是更好，如用在茅台上，但有时不行，如用在工行上

```{r}

symA="601818.SH"
x<-get(symA)
idx.excess <- grep(paste0("excess", return.nDay, "D"), names(x))
excessPlot(symA,symB,60)
chart.CumReturns(get(paste0("R",symA)))

ss<-x[,idx.excess]
ss<-cbind(cbind(ss,EMA(ss,n=10,wilder = T)),
          EMA(ss,n=30,wilder = T),
          SMA(ss,10),
          SMA(ss,30))
plot(ss,legend.loc=T)

##把回测换成EMA，看看回撤结果
symA="600519.SH"
for(symA in sym50){
symB="000016.SH"
strategy.ReturnRevert(symA,symB,r.nDay = 60,sma1.nDay = 10,sma2.nDay = 30,ifEMA = T)
  
}

```


3. 考虑计算excess数据，使用EMA曲线的波峰波谷的数量来作为判断好的曲线和不好的曲线
```{r}
source("./R/RelativeValueStgy.R")

```

1. 按相关性、距离

```{r}
symA="600028.SH"
x<-get(symA)
idx.excess <- grep(paste0("excess", return.nDay, "D"), names(x))
x<-x["2005/"]
acf(x[,idx.excess],lag.max=100,na.action = na.pass)

```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
