---
title: "R Notebook"
output: html_notebook
---

```{r}

source("./R/层次分析法用于相对价值.R")

myweight<-out["2012-7/"]

```
1. kmeans聚类
```{r}
k.clusters<-kmeans(myweight,5)
k.centers<-k.clusters$centers
k.centers[order(k.centers[,1]),]


```
无法区分50和创业板，因此不适用

2. 高斯聚类
```{r}
mod1<-Mclust(myweight)
summary(mod1)
plot(mod1,what=c("BIC","classification"))

```


3. 根据相对收益及其动量确定权重

```{r}
rm(list=ls())
source(file.path(substr(getwd(), 1, 22), "header.R"))
symA <- "000016.SH"
symB <- "399006.SZ"
r.nDay = 60
excessPlot(symA, symB, return.nDay = r.nDay)


applyInd(
  symA,
  fun.name = "leadX",
  arguments = list(
    x = get(symA),
    column = paste0("excess", r.nDay, "D"),
    k = 20
  ),
  label = paste0("leadcumR", 20, "D")
)

applyInd(
  symA,
  fun.name = "lagX",
  arguments = list(
    x = get(symA),
    column = paste0("excess", r.nDay, "D"),
    k = 20
  ),
  label = paste0("lagcumR", 20, "D")
)


applyInd(
  symA,
  fun.name = "minusX",
  arguments = list(
    x = get(symA),
    column1=paste0("leadcumR", 20, "D"),
    column2 = paste0("excess", r.nDay, "D")
  ),
  label = paste0("profit")
)


applyInd(
  sym = symA,
  fun.name = "apply.fromstartX",
  arguments = list(
    x = get(symA),
    column = paste0("excess", r.nDay, "D"),
    FUN = "last.percentile"
  ),
  label = "percent"
)

# applyInd(
#   sym = symA,
#   fun.name = "rollapplyX",
#   arguments = list(
#   x = get(symA),
#   column = paste0("excess", r.nDay, "D"),
#   width = 40,
#   FUN = "last.percentile"
#   ),
#   label = "momentum"
#   )

applyInd(
  symA,
  fun.name = "minusX",
  arguments = list(
    x = get(symA),
    column2=paste0("lagcumR", 20, "D"),
    column1 = paste0("excess", r.nDay, "D")
  ),
  label = paste0("momentum")
)





idname<-c("percent","momentum","profit")
idx<-match.names(idname,names(get(symA)))
xx<-get(symA)[,idx]
xx<-xx["2010/"]
xx<-as.data.frame(xx)
names(xx)<-idname

xx<-xx[!is.na(xx[,3]),]


ss<-xx%>%mutate(per.cut=cut(percent,seq(0,1,length.out = 6)),mom.cut=ifelse(momentum>0,1,-1))%>%group_by(mom.cut,per.cut)%>%
  summarise(mn=mean(profit),md=median(profit),num=n(),q1=quantile(profit,0.1),q2=quantile(profit,0.2),
            )
ss
tail(get(symA),40)

write.csv(ss,file="ss.csv")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
