---
title: "R Notebook"
output: html_notebook
---

```{r}

source("./R/层次分析法用于相对价值.R")

myweight<-out["2012-7/"]

```
1. kmeans聚类
```{r}
k.clusters<-kmeans(myweight,5)
k.centers<-k.clusters$centers
k.centers[order(k.centers[,1]),]


```
无法区分50和创业板，因此不适用

2. 高斯聚类
```{r}
mod1<-Mclust(myweight)
summary(mod1)
plot(mod1,what=c("BIC","classification"))

```


3. 根据相对收益及其动量确定权重

```{r}
rm(list=ls())
source(file.path(substr(getwd(), 1, 22), "header.R"))
symA <- "000016.SH"
symB <- "399006.SZ"
r.nDay = 60
profit.day=20
window=500
excessPlot(symA, symB, return.nDay = r.nDay)


applyInd(
  symA,
  fun.name = "leadX",
  arguments = list(
    x = get(symA),
    column = paste0("excess", r.nDay, "D"),
    k = profit.day
  ),
  label = paste0("leadcumR", profit.day, "D")
)

applyInd(
  symA,
  fun.name = "lagX",
  arguments = list(
    x = get(symA),
    column = paste0("excess", r.nDay, "D"),
    k = profit.day
  ),
  label = paste0("lagcumR", profit.day, "D")
)


applyInd(
  symA,
  fun.name = "minusX",
  arguments = list(
    x = get(symA),
    column1=paste0("leadcumR", profit.day, "D"),
    column2 = paste0("excess", r.nDay, "D")
  ),
  label = paste0("profit")
)

if(window>0){

  applyInd(
  sym = symA,
  fun.name = "rollapplyX",
  arguments = list(
    x = get(symA),
    column = paste0("excess", r.nDay, "D"),
    FUN = "last.percentile",
    width=window
  ),
  label = "percent"
)

    
}else{
  
applyInd(
  sym = symA,
  fun.name = "apply.fromstartX",
  arguments = list(
    x = get(symA),
    column = paste0("excess", r.nDay, "D"),
    FUN = "last.percentile"
  ),
  label = "percent"
)
  
  
}




# applyInd(
#   sym = symA,
#   fun.name = "rollapplyX",
#   arguments = list(
#   x = get(symA),
#   column = paste0("excess", r.nDay, "D"),
#   width = 40,
#   FUN = "last.percentile"
#   ),
#   label = "momentum"
#   )


PVtemp.fun<-function(x,column,thresh){
  
  x<-peakValleyY(x,column,thresh)
  id.p<-which(x==1)
  id.v<-which(x==-1)
  
  
  y<-cumsum(x)
  
  
  if(which(!is.na(id.p))[1]>which(!is.na(id.v))[1]){
    
      z<-ifelse(y==0,1,-1)
    
  }else{
    z<-ifelse(y==0,-1,1)
  }
  names(z)<-"momentum"
  z
}

applyInd(
  symA,
  fun.name = "PVtemp.fun",
  arguments = list(
    x = get(symA),
    column = paste0("excess", r.nDay, "D"),
    thresh=60
    
  ),
  label = paste0("momentum")
)




idname<-c("percent","momentum","profit")
idx<-match.names(idname,names(get(symA)))
xx<-get(symA)[,idx]
xx<-xx["2010/"]
xx<-as.data.frame(xx)
names(xx)<-idname

xx<-xx[complete.cases(xx),]

yy<-xx%>%mutate(per.cut=cut(percent,seq(0,1,length.out = 6)),mom.cut=ifelse(momentum>0,1,-1))

ggplot(yy,aes(profit))+facet_grid(per.cut~mom.cut)+geom_histogram(bins=100)

ss<-xx%>%mutate(per.cut=cut(percent,seq(0,1,length.out = 6)),mom.cut=ifelse(momentum>0,1,-1))%>%group_by(mom.cut,per.cut)%>%
  summarise(q1=quantile(profit,0.1),q2=quantile(profit,0.2),
            q3=quantile(profit,0.3),
            q4=quantile(profit,0.4),
            q5=quantile(profit,0.5),
            q6=quantile(profit,0.6),
            q7=quantile(profit,0.7),
            q8=quantile(profit,0.8),
            q9=quantile(profit,0.9),
            qX=quantile(profit,1),num=n())

ss
a1<-as.data.frame(sapply(ss[,-c(1,2)],rank))
a3=rowMeans(a1)
a0<-as.data.frame(ss[,c(1,2)])
cbind(a0,a1,a3)

profit<-as.vector(xx[,3])
type<-paste0(yy[,4],"-",yy[,5])
typeid<-unique(type)

gen.f<-function(w){
  
  n<-length(w)
  
  mylist<-vector(mode = "list",length = n)
  for(i in 1:n){
    
    
    mylist[[i]]<-w[i]*profit[which(type==typeid[i])]
    
  }
  ff<-unlist(mylist)
  
  fval<- -mean(ff)/sd(ff)
  return(fval)
  
  
}

startW<-rep(0,10)
ans<-optimx(startW,fn=gen.f,lower=rep(0,10),upper=rep(1,10),method="BFGS")



write.csv(ss,file="ss.csv")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
